---
title: "Untitled"
author: "Peiyao Zhu (Noel)"
date: "12/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('../Code/my_rf_cv.R')
library(ggplot2)
library(dplyr)
```

* Predict `body_mass_g` using covariates `bill_length_mm`, `bill_depth_mm`, and `flipper_length_mm`. 
* Iterate through `k` in  `c(2, 5, 10)`:
    * For each value of `k`, run your function $30$ times. 
    * For each of the $30$ iterations, store the CV estimated MSE.
```{r}
cv_estimate <- list()
trial <- 1
for (i in c(2, 5, 10)) {
  mse <- rep(NA, 30)
  for (j in 1:30) {
    mse[j] <- my_rf_cv(i)
  }
  cv_estimate[[trial]] <- mse
  trial <- trial + 1
}
```

* Use `ggplot2` with 3 boxplots to display these data in an informative way. There should be a boxplot associated with each value of `k`, representing $30$ simulations each.
```{r}
category <- c(rep("2", 30), rep("5", 30), rep("10", 30))
mse <- c(cv_estimate[[1]], cv_estimate[[2]], cv_estimate[[3]])
my_cv <- data.frame("k" = category, "CV_MSE" = mse)
mse_by_k <- ggplot(data = my_cv, aes(x = k, y = CV_MSE)) +
  geom_boxplot(aes(group = k), fill = "lightblue") +
  labs(title = "CV MSE by k value", 
       x = "", 
       y = "") +
  theme(plot.title =
          element_text(hjust = 0.5))
ggsave("mse_by_k.png", path = "../Output/Figures")
```

* Use a table to display the average CV estimate and the standard deviation of the CV estimates across $k$. Your table should have 3 rows (one for each value of $k$) and 2 columns (one for the mean and the other for the standard deviation).
```{r}
average_cv <- matrix(NA, nrow = 3, ncol = 2)
rownames(average_cv) <- c("k = 2", "k = 5", "k = 10")
colnames(average_cv) <- c("average CV MSE", "standard deviation")
average_cv[1, 1] <- mean(cv_estimate[[1]])
average_cv[1, 2] <- sd(cv_estimate[[1]])
average_cv[2, 1] <- mean(cv_estimate[[2]])
average_cv[2, 2] <- sd(cv_estimate[[2]])
average_cv[3, 1] <- mean(cv_estimate[[3]])
average_cv[3, 2] <- sd(cv_estimate[[3]])
average_cv <- as.data.frame(average_cv)
saveRDS(average_cv, file = "../Output/Results/summary_mse.rds")

all_mse <- cbind(cv_estimate[[1]], cv_estimate[[2]], cv_estimate[[3]])
colnames(all_mse) <- c("k = 2", "k = 5", "k = 10")
write.csv(all_mse, file = "../Output/Results/all_mse.csv")
```
